# Data Import and Environment Setup

```{r}
# Needed libraries
libs <- c("tidyverse", "ggplot2", "stringr", "ggcorrplot")
# Libraries installation
installed_libs <- libs %in% rownames(installed.packages())
if (any(installed_libs == FALSE)) {
    install.packages(libs[!installed_libs])
}
# Libraries loading
library(tidyverse)
library(ggplot2)
library(stringr)
library(ggcorrplot)
# Variable for storing the main data set
cheese <- read.csv("./dataset/cheese.csv")
# Variable for storing color scale
color_set <- scale_fill_manual(values = c(
  "#f0f", "#f08", "#f00", "#f80", "#ff0",
  "#8f0", "#0f0", "#0f8", "#0ff", "#08f",
  "#00f", "#80f"
))
color_set_2 <- scale_fill_manual(values = c(
  "#ff0", "#dd0", "#bb0", "#990", "#770",
  "#550", "#330", "#110"
))
theme_set <- theme(
  axis.text = element_text(color = "#999"),
  axis.title = element_text(color = "#999"),
  legend.background = element_rect(fill = "#333"),
  legend.title = element_text(color = "#999"),
  legend.text = element_text(color = "#999"),
  panel.background = element_rect(fill = "#444"),
  panel.grid = element_blank(),
  plot.background = element_rect(fill = "#444"),
  plot.title = element_text(color = "#999")
)
```

# Data Overview

## Unfiltered

The dataset showcases over a thousand different cheeses from all over the world, distinguishing them by various features like the type of milk that was used in the production process, the country and region of its origin as well as its producer, the family this particular cheese belongs to, fat and calcium contents, purely taste and consistency features like type, texture, rind, color, flavor and aroma, is it vegetarian or vegan and some vocabulary information like synonyms or alternative spellings.

```{r}
cheese
```

## Cheese Distribution by Country

This chart represents the cheeses divided into separate countries of origin. It is presented as a top 12 list to make the plot more readable, as there are plenty of countries present in the dataset. Over 1/4 of entries in this dataset originates from Unites States.

```{r}
# Data preparation
by_country <- cheese %>%
  filter(!is.na(cheese) & !is.na(country)) %>% 
  select(cheese, country) %>% 
  separate_rows(country, sep = ", ") %>% 
  distinct(cheese, country) %>% 
  group_by(country) %>% 
  summarise(count = n()) %>%
  arrange(desc(count)) %>% 
  head(n = 12)

by_country

# Plot creation
by_country_plot <- ggplot(
    data = by_country,
    aes(x = "", y = count, fill = reorder(country, count))
  ) +
  geom_col(color = "#444") + coord_polar(theta = "y") +
  labs(
    title = "Cheese Distribution by Country (top 12)",
    fill = "Countries",
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) +
  color_set + theme_set + xlab("") + ylab("Number of cheeses")

by_country_plot
```

## Cheese Families Distribution in USA

This plot is an extension to the previous one, providing more insights to the diversity of cheeses available in the United States. It represents different cheese families that are present in USA regions. Same as previously, it is limited to top 12 families to provide better readability. There are three main families including Cheddar, Blue and Brie cheeses.

```{r}
# Data preparation
families_by_region_usa <- cheese %>%
  filter(!is.na(family) & !is.na(region) & country == "United States") %>% 
  select(family, region) %>% 
  separate_rows(region, sep = ", ") %>% 
  distinct(family, region) %>% 
  group_by(family) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(n = 12)

families_by_region_usa

# Plot creation
families_by_region_usa_plot <- ggplot(
    data = families_by_region_usa,
    aes(x = reorder(family, -count), y = count, fill = reorder(family, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Families Distribution in USA (top 12)",
    fill = "Families"
  ) + color_set + theme_set + xlab("") + ylab("Number of cheeses") +
  theme(axis.text.x = element_blank())
  
families_by_region_usa_plot
```

## Cheese Families Distribution in France

This chart aims to determine whether there are any similarities between the countries that are leading in the cheese market. For this plot we switch to France. Results show that the diversity is much smaller compared to previous outcome but the most common cheese families are Brie, Camembert and Blue, making it very similar to United States podium.

```{r}
# Data preparation
families_by_region_france <- cheese %>%
  filter(!is.na(family) & !is.na(region) & country == "France") %>% 
  select(family, region) %>% 
  separate_rows(region, sep = ", ") %>% 
  distinct(family, region) %>% 
  group_by(family) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(n = 12)

families_by_region_france

# Plot creation
families_by_region_france_plot <- ggplot(
    data = families_by_region_france,
    aes(x = reorder(family, -count), y = count, fill = reorder(family, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Families Distribution in France",
    fill = "Families"
  ) + color_set + theme_set + xlab("") + ylab("Number of cheeses") +
  theme(axis.text.x = element_blank())
  
families_by_region_france_plot
```

## Cheese Families Distribution in Italy

To go over at least the half of the available records in the dataset we double check the most popular families, but this time in Italy. The diversity is slightly bigger than in France but still nowhere near USA. However the most common families available in Italy differ when compared to the two previous results. allowing for a statement that different regions around world prefer different cheese families.

```{r}
# Data preparation
families_by_region_italy <- cheese %>%
  filter(!is.na(family) & !is.na(region) & country == "Italy") %>% 
  select(family, region) %>% 
  separate_rows(region, sep = ", ") %>% 
  distinct(family, region) %>% 
  group_by(family) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(n = 12)

families_by_region_italy

# Plot creation
families_by_region_italy_plot <- ggplot(
    data = families_by_region_italy,
    aes(x = reorder(family, -count), y = count, fill = reorder(family, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Families Distribution in Italy",
    fill = "Families"
  ) + color_set + theme_set + xlab("") + ylab("Number of cheeses") +
  theme(axis.text.x = element_blank())
  
families_by_region_italy_plot
```

## Cheese Distribution by Fat Content

This plot groups cheese based on the fat content, presenting a graphical representation of the products available on the market. Results show that majority of cheeses have their fat content around 40%.

```{r}
# Data preparation
by_fat_content <- cheese %>%
  filter(!is.na(cheese) & !is.na(fat_content)) %>% 
  select(cheese, fat_content) %>% 
  distinct(cheese, fat_content) %>% 
  mutate(
    fat_content = ifelse(
      str_detect(fat_content, "g/100g"),
      str_replace(fat_content, " g/100g", "%"),
      fat_content
    )
  ) %>%
  filter(!str_detect(fat_content, "-")) %>% 
  mutate(
    fat_content = str_remove(fat_content, "%"),
    fat_content = as.numeric(fat_content)
  ) %>% 
  arrange(desc(fat_content))

breaks <- seq(0, ceiling(max(by_fat_content$fat_content) / 6.66) * 6.66, by = 6.66)

by_fat_content <- by_fat_content %>%
  mutate(fat_content_group = cut(fat_content, breaks = breaks, include.lowest = TRUE, right = FALSE)) %>% 
  group_by(fat_content_group) %>% 
  summarise(count = n())

by_fat_content

# Plot creation
by_fat_content_plot <- ggplot(
    data = by_fat_content,
    aes(x = fat_content_group, y = count, fill = fat_content_group)
  ) +
  geom_col() + 
  labs(
    title = "Cheese Distribution by Fat Content",
    fill = "Fat Content Range (%)"
  ) +
  color_set + theme_set + xlab("Fat Content Groups") + ylab("Number of cheeses") +
  theme(axis.text.x = element_blank())
  
by_fat_content_plot
```

## Cheese Distribution by Calcium Content

Similarly to the previous plot this one provides general information on the market available cheeses, but this time it is about average calcium amount. Outcome shows that the pattern of Gaussian distribution is preserved. Most cheeses score between 400 and 500 mg of calcium per 100g of cheese.

```{r}
# Data preparation
by_calcium_content <- cheese %>%
  filter(!is.na(cheese) & !is.na(calcium_content)) %>% 
  select(cheese, calcium_content) %>% 
  distinct(cheese, calcium_content) %>% 
  filter(!str_detect(calcium_content, "-")) %>% 
  mutate(
    calcium_content = str_remove(calcium_content, " mg/100g"),
    calcium_content = as.numeric(calcium_content)
  ) %>% 
  arrange(desc(calcium_content))

breaks <- seq(0, ceiling(max(by_calcium_content$calcium_content) / 100) * 100, by = 100)

by_calcium_content <- by_calcium_content %>%
  mutate(calcium_content_group = cut(calcium_content, breaks = breaks, include.lowest = TRUE, right = FALSE)) %>% 
  group_by(calcium_content_group) %>% 
  summarise(count = n())

by_calcium_content

# Plot creation
by_calcium_content_plot <- ggplot(
    data = by_calcium_content,
    aes(x = calcium_content_group, y = count, fill = calcium_content_group)
  ) +
  geom_col() + 
  labs(
    title = "Cheese Distribution by Calcium Content",
    fill = "Calcium Content Range (mg/100g)"
  ) + color_set + theme_set +
  xlab("Calcium Content Groups") + ylab("Number of cheeses") +
  theme(axis.text.x = element_blank())
  
by_calcium_content_plot
```

## Calcium Content / Fat Content Dependence

This chart aims to detect the dependence between fat and calcium content of different cheeses. To achieve this we prepared a scatter point plot with a trend line. With the removal of extreme values in the dataset it can be seen that fat and calcium levels are rising linearly up to certain point. After that with even bigger increase in calcium, the percentage of fat start to drop.

```{r}
calcium_vs_fat <- cheese %>%
  filter(!is.na(cheese) & !is.na(fat_content) & !is.na(calcium_content)) %>% 
  select(fat_content, calcium_content) %>% 
  distinct(fat_content, calcium_content) %>% 
  mutate(
    fat_content = ifelse(
      str_detect(fat_content, "%"),
      str_replace(fat_content, "%", " g/100g"),
      fat_content
    )
  ) %>%
  filter(!str_detect(fat_content, "-")) %>% 
  mutate(
    fat_content = str_remove(fat_content, " g/100g"),
    fat_content = as.numeric(fat_content),
    calcium_content = str_remove(calcium_content, " mg/100g"),
    calcium_content = as.numeric(calcium_content)
  ) %>% 
  filter(calcium_content < 2000)

calcium_vs_fat

# Plot creation
calcium_vs_fat_plot <- ggplot(
    data = calcium_vs_fat,
    aes(x = calcium_content, y = fat_content)
  ) +
  geom_point(color = "#999", ) +
  geom_smooth(color = "#666", se = FALSE, method = "loess") +
  labs(
    title = "Calcium Content / Fat Content Dependence",
    x = "Calcium Content (mg/100g)",
    y = "Fat Content (g/100g)",
  ) +
  theme_set +
  theme(
    axis.text = element_text(color = "#999"),
    axis.title = element_text(color = "#999"),
    panel.grid.minor = element_line(color = "#666", linetype = "dashed"),
    panel.grid.major = element_line(color = "#666", linetype = "dashed")
  )
  
calcium_vs_fat_plot
```

## Vegetarian and Vegan Cheese Availability

This plot presents the relation between vegan and vegetarian category of cheese. Results show that there are very little vegan cheeses available on the market, but the ratio between regular and vegetarian is close to 1:1 with slight advantage to the regular cheese.

```{r}
#Data preparation
vegetarian_vs_vegan <- cheese %>%
  filter(!is.na(cheese) & !is.na(vegetarian), !is.na(vegan)) %>%
  select(cheese, vegetarian, vegan) %>%
  distinct(cheese, vegetarian, vegan) %>%
  mutate(group = ifelse(
    str_detect(vegetarian, "FALSE") & str_detect(vegan, "FALSE"),
    "Neither",
    ifelse(
      str_detect(vegan, "TRUE"),
      "Vegan",
      "Vegetarian")
    )
  ) %>%
  group_by(group) %>%
  summarise(count = n()) %>%
## Sorting the data
  arrange(desc(count))

vegetarian_vs_vegan

#Plot creation
vegetarian_vs_vegan_plot <- ggplot(
    data = vegetarian_vs_vegan,
    aes(x = "", y = count, fill = reorder(group, count))
  ) +
  geom_col(color = "#444") + coord_polar(theta = "y") +
  labs(
    title = "Vegetarian and Vegan Cheese Availability",
    fill = "Cheese Type"
  ) + theme_set + xlab("") + ylab("Number of cheeses")

vegetarian_vs_vegan_plot
```

Starting from the next plot, we are going to delve deeper into different countries preferences, namely cheese texture, flavor, milk used and producers. To make the charts more interesting, we added division for country regions in the form of stacked bars.

## Popular Cheese Textures in United States

```{r}
# Data preparation
texture_by_region_usa <- cheese %>%
  filter(!is.na(texture) & !is.na(region) & country == "United States") %>%
  select(texture, region) %>%
  separate_rows(texture, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(texture, region) %>%
  summarise(count = n()) %>%
  filter(count > 6)

texture_by_region_usa

# Plot creation
texture_by_region_usa_plot <- ggplot(
    data = texture_by_region_usa,
    aes(x = count, y = reorder(region, desc(region)), fill = texture)
  ) + geom_col() + 
  labs(
    title = "Popular Cheese Textures in United States",
    fill = "Textures"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
  
texture_by_region_usa_plot
```

## Popular Cheese Flavors in United States

```{r}
# Data preparation
flavor_by_region_usa <- cheese %>%
  filter(!is.na(flavor) & !is.na(region) & country == "United States") %>%
  select(flavor, region) %>%
  separate_rows(flavor, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(flavor, region) %>%
  summarise(count = n()) %>% 
  filter(count > 8)

flavor_by_region_usa

# Plot creation
flavor_by_region_usa_plot <- ggplot(
    data = flavor_by_region_usa,
    aes(x = count, y = reorder(region, desc(region)), fill = flavor)
  ) + geom_col() + 
  labs(
    title = "Popular Cheese Flavors in United States",
    fill = "Flavors"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
  
flavor_by_region_usa_plot
```

## Top Cheese Producers in United States

```{r}
# Data preparation
producers_by_region_usa <- cheese %>%
  filter(!is.na(producers) & !is.na(region) & country == "United States") %>%
  select(producers, region) %>%
  separate_rows(producers, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(producers, region) %>%
  summarise(count = n()) %>%
  filter(count > 7)

producers_by_region_usa

# Plot creation
producers_by_region_usa_plot <- ggplot(
    data = producers_by_region_usa,
    aes(x = count, y = reorder(region, desc(region)), fill = producers)
  ) + geom_col() + 
  labs(
    title = "Top Cheese Producers in United States",
    fill = "Producers"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
  
producers_by_region_usa_plot
```

## Milk Type Popularity in United States

```{r}
# Data preparation
milk_by_region_usa <- cheese %>%
  filter(!is.na(milk) & !is.na(region) & country == "United States") %>%
  select(milk, region) %>%
  separate_rows(milk, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(milk, region) %>%
  summarise(count = n()) %>%
  filter(count > 2)

milk_by_region_usa

# Plot creation
milk_by_region_usa_plot <- ggplot(
    data = milk_by_region_usa,
    aes(x = count, y = reorder(region, desc(region)), fill = milk)
  ) + geom_col() +
  labs(
    title = "Milk Type Popularity in United States",
    fill = "Milk Type"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
  
milk_by_region_usa_plot
```

## Cheese Colors Popularity in United States

```{r}
# Data preparation
color_by_region_usa <- cheese %>%
  filter(!is.na(color) & !is.na(region) & country == "United States") %>%
  select(color, region) %>%
  separate_rows(color, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(color, region) %>%
  summarise(count = n()) %>%
  filter(count > 1)

color_by_region_usa

# Plot creation
color_by_region_usa_plot <- ggplot(
    data = color_by_region_usa,
    aes(x = count, y = reorder(region, desc(region)), fill = color)
  ) + geom_col() +
  labs(
    title = "Cheese Colors Popularity in United States",
    fill = "Cheese Colors"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
        
color_by_region_usa_plot
```

## Cheese Rinds Popularity in United States

```{r}
# Data preparation
rind_by_region_usa <- cheese %>%
  filter(!is.na(rind) & !is.na(region) & country == "United States") %>%
  select(rind, region) %>%
  separate_rows(rind, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(rind, region) %>%
  summarise(count = n()) %>%
  filter(count > 1)

rind_by_region_usa

# Plot creation
rind_by_region_usa_plot <- ggplot(
    data = rind_by_region_usa,
    aes(x = count, y = reorder(region, desc(region)), fill = rind)
  ) + geom_col() +
  labs(
    title = "Cheese Rinds Popularity in United States",
    fill = "Cheese Rinds"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
        
rind_by_region_usa_plot
```

## Popular Cheese Textures in France

```{r}
# Data preparation
texture_by_region_france <- cheese %>%
  filter(!is.na(texture) & !is.na(region) & country == "France") %>%
  select(texture, region) %>%
  separate_rows(texture, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(texture, region) %>%
  summarise(count = n()) %>%
  filter(count > 1)

texture_by_region_france

# Plot creation
texture_by_region_france_plot <- ggplot(
    data = texture_by_region_france,
    aes(x = count, y = reorder(region, desc(region)), fill = texture)
  ) + geom_col() + 
  labs(
    title = "Popular Cheese Textures in France",
    fill = "Textures"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
  
texture_by_region_france_plot
```

## Popular Cheese Flavors in France

For this plot we had to change the default coloring scale due to the fact that French cheeses are very different in their flavors.

```{r}
# Data preparation
flavor_by_region_france <- cheese %>%
  filter(!is.na(flavor) & !is.na(region) & country == "France") %>%
  select(flavor, region) %>%
  separate_rows(flavor, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(flavor, region) %>%
  summarise(count = n()) %>% 
  filter(count > 1)

flavor_by_region_france

# Plot creation
flavor_by_region_france_plot <- ggplot(
    data = flavor_by_region_france,
    aes(x = count, y = reorder(region, desc(region)), fill = flavor)
  ) + geom_col() + 
  labs(
    title = "Popular Cheese Flavors in France",
    fill = "Flavors"
  ) + theme_set + xlab("Number of cheeses") + ylab("Regions")
  
flavor_by_region_france_plot
```

## Top Cheese Producers in France

For this plot we had to discard our own color scheme and trim the results list because the dataset showcases that France has a lot of cheese producers and pretty much every one of them make only one cheese.

```{r}
# Data preparation
producers_by_region_france <- cheese %>%
  filter(!is.na(producers) & !is.na(region) & country == "France") %>%
  select(producers, region) %>%
  separate_rows(producers, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(producers, region) %>%
  summarise(count = n()) %>% 
  head(n = 15)

producers_by_region_france

# Plot creation
producers_by_region_france_plot <- ggplot(
    data = producers_by_region_france,
    aes(x = count, y = reorder(region, desc(region)), fill = producers)
  ) + geom_col() + 
  labs(
    title = "Top Cheese Producers in France",
    fill = "Producers"
  ) + theme_set + xlab("Number of cheeses") + ylab("Regions")
  
producers_by_region_france_plot
```

## Milk Type Popularity in France

```{r}
# Data preparation
milk_by_region_france <- cheese %>%
  filter(!is.na(milk) & !is.na(region) & country == "France") %>%
  select(milk, region) %>%
  separate_rows(milk, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(milk, region) %>%
  summarise(count = n()) %>%
  filter(count > 1)

milk_by_region_france

# Plot creation
milk_by_region_france_plot <- ggplot(
    data = milk_by_region_france,
    aes(x = count, y = reorder(region, desc(region)), fill = milk)
  ) + geom_col() +
  labs(
    title = "Milk Type Popularity in France",
    fill = "Milk Type"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
  
milk_by_region_france_plot
```

## Cheese Colors Popularity in France

For this plot we had to again shorten the data output as the dataset presents that France offers a variety of cheese colors changing dependently of the region.

```{r}
# Data preparation
color_by_region_france <- cheese %>%
  filter(!is.na(color) & !is.na(region) & country == "France") %>%
  select(color, region) %>%
  separate_rows(color, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(color, region) %>%
  summarise(count = n()) %>%
  head(n = 15)

color_by_region_france

# Plot creation
color_by_region_france_plot <- ggplot(
    data = color_by_region_france,
    aes(x = count, y = reorder(region, desc(region)), fill = color)
  ) + geom_col() +
  labs(
    title = "Cheese Colors Popularity in France",
    fill = "Cheese Colors"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
        
color_by_region_france_plot
```

## Cheese Rinds Popularity in France

```{r}
# Data preparation
rind_by_region_france <- cheese %>%
  filter(!is.na(rind) & !is.na(region) & country == "France") %>%
  select(rind, region) %>%
  separate_rows(rind, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(rind, region) %>%
  summarise(count = n()) %>%
  filter(count > 1)

rind_by_region_france

# Plot creation
rind_by_region_france_plot <- ggplot(
    data = rind_by_region_france,
    aes(x = count, y = reorder(region, desc(region)), fill = rind)
  ) + geom_col() +
  labs(
    title = "Cheese Rinds Popularity in France",
    fill = "Cheese Rinds"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
        
rind_by_region_france_plot
```

## Popular Cheese Textures in Italy

```{r}
# Data preparation
texture_by_region_italy <- cheese %>%
  filter(!is.na(texture) & !is.na(region) & country == "Italy") %>%
  select(texture, region) %>%
  separate_rows(texture, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(texture, region) %>%
  summarise(count = n()) %>%
  filter(count > 4)

texture_by_region_italy

# Plot creation
texture_by_region_italy_plot <- ggplot(
    data = texture_by_region_italy,
    aes(x = count, y = reorder(region, desc(region)), fill = texture)
  ) + geom_col() + 
  labs(
    title = "Popular Cheese Textures in Italy",
    fill = "Textures"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
  
texture_by_region_italy_plot
```

## Popular Cheese Flavors in Italy

```{r}
# Data preparation
flavor_by_region_italy <- cheese %>%
  filter(!is.na(flavor) & !is.na(region) & country == "Italy") %>%
  select(flavor, region) %>%
  separate_rows(flavor, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(flavor, region) %>%
  summarise(count = n()) %>% 
  filter(count > 4)

flavor_by_region_italy

# Plot creation
flavor_by_region_italy_plot <- ggplot(
    data = flavor_by_region_italy,
    aes(x = count, y = reorder(region, desc(region)), fill = flavor)
  ) + geom_col() + 
  labs(
    title = "Popular Cheese Flavors in Italy",
    fill = "Flavors"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
  
flavor_by_region_italy_plot
```

## Top Cheese Producers in Italy

```{r}
# Data preparation
producers_by_region_italy <- cheese %>%
  filter(!is.na(producers) & !is.na(region) & country == "Italy") %>%
  select(producers, region) %>%
  separate_rows(producers, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(producers, region) %>%
  summarise(count = n()) %>%
  filter(count > 1)

producers_by_region_italy

# Plot creation
producers_by_region_italy_plot <- ggplot(
    data = producers_by_region_italy,
    aes(x = count, y = reorder(region, desc(region)), fill = producers)
  ) + geom_col() + 
  labs(
    title = "Top Cheese Producers in Italy",
    fill = "Producers"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
  
producers_by_region_italy_plot
```

## Milk Type Popularity in Italy

```{r}
# Data preparation
milk_by_region_italy <- cheese %>%
  filter(!is.na(milk) & !is.na(region) & country == "Italy") %>%
  select(milk, region) %>%
  separate_rows(milk, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(milk, region) %>%
  summarise(count = n()) %>%
  filter(count > 1)

milk_by_region_italy

# Plot creation
milk_by_region_italy_plot <- ggplot(
    data = milk_by_region_italy,
    aes(x = count, y = reorder(region, desc(region)), fill = milk)
  ) + geom_col() +
  labs(
    title = "Milk Type Popularity in Italy",
    fill = "Milk Type"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
        
milk_by_region_italy_plot
```

## Cheese Colors Popularity in Italy

```{r}
# Data preparation
color_by_region_italy <- cheese %>%
  filter(!is.na(color) & !is.na(region) & country == "Italy") %>%
  select(color, region) %>%
  separate_rows(color, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(color, region) %>%
  summarise(count = n()) %>%
  filter(count > 1)

color_by_region_italy

# Plot creation
color_by_region_italy_plot <- ggplot(
    data = color_by_region_italy,
    aes(x = count, y = reorder(region, desc(region)), fill = color)
  ) + geom_col() +
  labs(
    title = "Cheese Colors Popularity in Italy",
    fill = "Cheese Colors"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
        
color_by_region_italy_plot
```

## Cheese Rinds Popularity in Italy

```{r}
# Data preparation
rind_by_region_italy <- cheese %>%
  filter(!is.na(rind) & !is.na(region) & country == "Italy") %>%
  select(rind, region) %>%
  separate_rows(rind, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  group_by(rind, region) %>%
  summarise(count = n()) %>%
  filter(count > 1)

rind_by_region_italy

# Plot creation
rind_by_region_italy_plot <- ggplot(
    data = rind_by_region_italy,
    aes(x = count, y = reorder(region, desc(region)), fill = rind)
  ) + geom_col() +
  labs(
    title = "Cheese Rinds Popularity in Italy",
    fill = "Cheese Rinds"
  ) + color_set_2 + theme_set + xlab("Number of cheeses") + ylab("Regions")
        
rind_by_region_italy_plot
```

Performing this analysis of the regional cheeses details has driven us to the conclusions that United States have the most products to offer, mostly due to the fact of being the largest country investigated in this research. France on the other hand has the most stable distribution of products depending on the region and that is most likely caused by the very large number of cheese producers divided around the country. Italy is an example of a balance between the two previous cases providing decent amounts of different cheeses while also maintaining the regional diversity of products.
