# Data Import and Environment Setup

```{r}
# Needed libraries
libs <- c("tidyverse", "ggplot2", "stringr")
# Libraries installation
installed_libs <- libs %in% rownames(installed.packages())
if (any(installed_libs == FALSE)) {
    install.packages(libs[!installed_libs])
}
# Libraries loading
library(tidyverse)
library(ggplot2)
library(stringr)
# Variable for storing the main data set
cheese <- read.csv("./dataset/cheese.csv")
# Variable for storing color scale
color_set <- scale_fill_manual(values = c(
  "#f0f", "#f08", "#f00", "#f80", "#ff0",
  "#8f0", "#0f0", "#0f8", "#0ff", "#08f",
  "#00f", "#80f"
))
theme_set <- theme(
  axis.text = element_blank(),
  axis.title = element_blank(),
  legend.background = element_rect(fill = "#444"),
  legend.title = element_text(color = "#999"),
  legend.text = element_text(color = "#999"),
  panel.background = element_rect(fill = "#444"),
  panel.grid = element_blank(),
  plot.background = element_rect(fill = "#444"),
  plot.title = element_text(color = "#999")
)
```

# Data Overview

## Unfiltered

The dataset showcases over a thousand different cheeses from all over the world, distinguishing them by various features like the type of milk that was used in the production process, the country and region of its origin as well as its producer, the family this particular cheese belongs to, fat and calcium contents, purely taste and consistency features like type, texture, rind, color, flavor and aroma, is it vegetarian or vegan and some vocabulary information like synonyms or alternative spellings.

```{r}
cheese
```

## Cheese Distribution by Country

This chart represents the cheeses divided into separate countries of origin. It is presented as a top 12 list to make the plot more readable, as there are plenty of countries present in the dataset. Over 1/4 of entries in this dataset originates from Unites States.

```{r}
# Data preparation
by_country <- cheese %>%
  filter(!is.na(cheese) & !is.na(country)) %>% 
  select(cheese, country) %>% 
  separate_rows(country, sep = ", ") %>% 
  distinct(cheese, country) %>% 
  group_by(country) %>% 
  summarise(count = n()) %>%
  arrange(desc(count)) %>% 
  head(n = 12)

by_country

# Plot creation
by_country_plot <- ggplot(
    data = by_country,
    aes(x = "", y = count, fill = reorder(country, count))
  ) +
  geom_col(color = "#444") + coord_polar(theta = "y") +
  labs(
    title = "Cheese Distribution by Country (top 12)",
    fill = "Countries",
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) +
  color_set + theme_set +
  theme(axis.text.x = element_text(color = "#999"))

by_country_plot
```

## Cheese Families Distribution by USA Regions

This plot is an extension to the previous one, providing more insights to the diversity of cheeses available in the United States. It represents different cheese families that are present in USA regions. Same as previously, it is limited to top 12 families to provide better readability. There are three main families including Cheddar, Blue and Brie cheeses.

```{r}
# Data preparation
families_by_region_usa <- cheese %>%
  filter(!is.na(family) & !is.na(region) & country == "United States") %>% 
  select(family, region) %>% 
  separate_rows(region, sep = ", ") %>% 
  distinct(family, region) %>% 
  group_by(family) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(n = 12)

families_by_region_usa

# Plot creation
families_by_region_usa_plot <- ggplot(
    data = families_by_region_usa,
    aes(x = reorder(family, -count), y = count, fill = reorder(family, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Families Distribution by USA Regions (top 12)",
    fill = "Families"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
families_by_region_usa_plot
```

## Cheese Families Distribution by France Regions

This chart aims to determine whether there are any similarities between the countries that are leading in the cheese market. For this plot we switch to France. Results show that the diversity is much smaller compared to previous outcome but the most common cheese families are Brie, Camembert and Blue, making it very similar to United States podium.

```{r}
# Data preparation
families_by_region_france <- cheese %>%
  filter(!is.na(family) & !is.na(region) & country == "France") %>% 
  select(family, region) %>% 
  separate_rows(region, sep = ", ") %>% 
  distinct(family, region) %>% 
  group_by(family) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(n = 12)

families_by_region_france

# Plot creation
families_by_region_france_plot <- ggplot(
    data = families_by_region_france,
    aes(x = reorder(family, -count), y = count, fill = reorder(family, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Families Distribution by France Regions",
    fill = "Families"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
families_by_region_france_plot
```

## Cheese Families Distribution by Italy Regions

To go over at least the half of the available records in the dataset we double check the most popular families, but this time in Italy. The diversity is slightly bigger than in France but still nowhere near USA. However the most common families available in Italy differ when compared to the two previous results. allowing for a statement that different regions around world prefer different cheese families.

```{r}
# Data preparation
families_by_region_italy <- cheese %>%
  filter(!is.na(family) & !is.na(region) & country == "Italy") %>% 
  select(family, region) %>% 
  separate_rows(region, sep = ", ") %>% 
  distinct(family, region) %>% 
  group_by(family) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(n = 12)

families_by_region_italy

# Plot creation
families_by_region_italy_plot <- ggplot(
    data = families_by_region_italy,
    aes(x = reorder(family, -count), y = count, fill = reorder(family, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Families Distribution by Italy Regions",
    fill = "Families"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
families_by_region_italy_plot
```

## Cheese Distribution by Fat Content

This plot groups cheese based on the fat content, presenting a graphical representation of the products available on the market. Results show that majority of cheeses have their fat content around 40%.

```{r}
# Data preparation
by_fat_content <- cheese %>%
  filter(!is.na(cheese) & !is.na(fat_content)) %>% 
  select(cheese, fat_content) %>% 
  distinct(cheese, fat_content) %>% 
  mutate(
    fat_content = ifelse(
      str_detect(fat_content, "g/100g"),
      str_replace(fat_content, " g/100g", "%"),
      fat_content
    )
  ) %>%
  filter(!str_detect(fat_content, "-")) %>% 
  mutate(
    fat_content = str_remove(fat_content, "%"),
    fat_content = as.numeric(fat_content)
  ) %>% 
  arrange(desc(fat_content))

breaks <- seq(0, ceiling(max(by_fat_content$fat_content) / 6.66) * 6.66, by = 6.66)

by_fat_content <- by_fat_content %>%
  mutate(fat_content_group = cut(fat_content, breaks = breaks, include.lowest = TRUE, right = FALSE)) %>% 
  group_by(fat_content_group) %>% 
  summarise(count = n())

by_fat_content

# Plot creation
by_fat_content_plot <- ggplot(
    data = by_fat_content,
    aes(x = fat_content_group, y = count, fill = fat_content_group)
  ) +
  geom_col() + 
  labs(
    title = "Cheese Distribution by Fat Content",
    fill = "Fat Content Range (%)"
  ) +
  color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
by_fat_content_plot
```

## Cheese Distribution by Calcium Content

Similarly to the previous plot this one provides general information on the market available cheeses, but this time it is about average calcium amount. Outcome shows that the pattern of Gaussian distribution is preserved. Most cheeses score between 400 and 500 mg of calcium per 100g of cheese.

```{r}
# Data preparation
by_calcium_content <- cheese %>%
  filter(!is.na(cheese) & !is.na(calcium_content)) %>% 
  select(cheese, calcium_content) %>% 
  distinct(cheese, calcium_content) %>% 
  filter(!str_detect(calcium_content, "-")) %>% 
  mutate(
    calcium_content = str_remove(calcium_content, " mg/100g"),
    calcium_content = as.numeric(calcium_content)
  ) %>% 
  arrange(desc(calcium_content))

breaks <- seq(0, ceiling(max(by_calcium_content$calcium_content) / 100) * 100, by = 100)

by_calcium_content <- by_calcium_content %>%
  mutate(calcium_content_group = cut(calcium_content, breaks = breaks, include.lowest = TRUE, right = FALSE)) %>% 
  group_by(calcium_content_group) %>% 
  summarise(count = n())

by_calcium_content

# Plot creation
by_calcium_content_plot <- ggplot(
    data = by_calcium_content,
    aes(x = calcium_content_group, y = count, fill = calcium_content_group)
  ) +
  geom_col() + 
  labs(
    title = "Cheese Distribution by Calcium Content",
    fill = "Calcium Content Range (mg/100g)"
  ) +
  color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
by_calcium_content_plot
```

## Calcium Content / Fat Content Dependence

This chart aims to detect the dependence between fat and calcium content of different cheeses. To achieve this we prepared a scatter point plot with a trend line. With the removal of extreme values in the dataset it can be seen that fat and calcium levels are rising linearly up to certain point. After that with even bigger increase in fat, the amounts of calcium start to drop.

```{r}
calcium_vs_fat <- cheese %>%
  filter(!is.na(cheese) & !is.na(fat_content) & !is.na(calcium_content)) %>% 
  select(cheese, fat_content, calcium_content) %>% 
  distinct(cheese, fat_content, calcium_content) %>% 
  mutate(
    fat_content = ifelse(
      str_detect(fat_content, "%"),
      str_replace(fat_content, "%", " g/100g"),
      fat_content
    )
  ) %>%
  filter(!str_detect(fat_content, "-")) %>% 
  mutate(
    fat_content = str_remove(fat_content, " g/100g"),
    fat_content = as.numeric(fat_content),
    calcium_content = str_remove(calcium_content, " mg/100g"),
    calcium_content = as.numeric(calcium_content)
  ) %>% 
  filter(calcium_content < 2000)

calcium_vs_fat

# Plot creation
calcium_vs_fat_plot <- ggplot(
    data = calcium_vs_fat,
    aes(x = calcium_content, y = fat_content)
  ) +
  geom_point(color = "#999") +
  geom_smooth(color = "#666", se = FALSE) +
  labs(
    title = "Calcium Content / Fat Content Dependence",
    x = "Calcium Content (mg/100g)",
    y = "Fat Content (g/100g)",
  ) +
  theme_set +
  theme(
    axis.text = element_text(color = "#999"),
    axis.title = element_text(color = "#999"),
    panel.grid.minor = element_line(color = "#666", linetype = "dashed"),
    panel.grid.major = element_line(color = "#666", linetype = "dashed")
  )
  
calcium_vs_fat_plot
```

## Vegetarian and Vegan Cheese Availability

This plot presents the relation between vegan and vegetarian category of cheese. Results show that there are very little vegan cheeses available on the market, but the ratio between regular and vegetarian is close to 1:1 with slight advantage to the regular cheese.

```{r}
#Data preparation
vegetarian_vs_vegan <- cheese %>%
  filter(!is.na(cheese) & !is.na(vegetarian), !is.na(vegan)) %>%
  select(cheese, vegetarian, vegan) %>%
  distinct(cheese, vegetarian, vegan) %>%
  mutate(group = ifelse(
    str_detect(vegetarian, "FALSE") & str_detect(vegan, "FALSE"),
    "Neither",
    ifelse(
      str_detect(vegan, "TRUE"),
      "Vegan",
      "Vegetarian")
    )
  ) %>%
  group_by(group) %>%
  summarise(count = n()) %>%
## Sorting the data
  arrange(desc(count))

vegetarian_vs_vegan

#Plot creation
vegetarian_vs_vegan_plot <- ggplot(
    data = vegetarian_vs_vegan,
    aes(x = "", y = count, fill = reorder(group, count))
  ) +
  geom_col(color = "#444") + coord_polar(theta = "y") +
  labs(
    title = "Vegetarian and Vegan Cheese Availability",
    fill = "Cheese Type"
  ) +
  theme_set + theme(
    axis.text.x = element_text(color = "#999")
  )

vegetarian_vs_vegan_plot
```

## Cheese Texture Popularity in USA Regions

Starting from this plot we are going to delve deeper into specific countries preferences. This chart focuses on different texture availability in Unites States. ...

```{r}
# Data preparation
texture_by_region_usa <- cheese %>%
  filter(!is.na(texture) & !is.na(region) & country == "United States") %>%
  select(texture, region) %>%
  separate_rows(texture, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(texture, region) %>% 
  group_by(texture) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

texture_by_region_usa

# Plot creation
texture_by_region_usa_plot <- ggplot(
    data = texture_by_region_usa,
    aes(x = reorder(texture, -count), y = count, fill = reorder(texture, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Textures Popularity in USA Regions",
    fill = "Textures"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
texture_by_region_usa_plot
```

## Cheese Flavor Popularity in USA Regions

```{r}
# Data preparation
flavor_by_region_usa <- cheese %>%
  filter(!is.na(flavor) & !is.na(region) & country == "United States") %>%
  select(flavor, region) %>%
  separate_rows(flavor, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(flavor, region) %>% 
  group_by(flavor) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

flavor_by_region_usa

# Plot creation
flavor_by_region_usa_plot <- ggplot(
    data = flavor_by_region_usa,
    aes(x = reorder(flavor, -count), y = count, fill = reorder(flavor, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Flavor Popularity in USA Regions",
    fill = "Flavors"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
flavor_by_region_usa_plot
```

## Top Cheese Producers in USA Regions

```{r}
# Data preparation
producers_by_region_usa <- cheese %>%
  filter(!is.na(producers) & !is.na(region) & country == "United States") %>%
  select(producers, region) %>%
  separate_rows(producers, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(producers, region) %>% 
  group_by(producers) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

producers_by_region_usa

# Plot creation
producers_by_region_usa_plot <- ggplot(
    data = producers_by_region_usa,
    aes(x = reorder(producers, -count), y = count, fill = reorder(producers, -count))
  ) + geom_col() + 
  labs(
    title = "Top Cheese Producers in USA Regions",
    fill = "Producers"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
producers_by_region_usa_plot
```

## Milk Type Usage in USA Regions

```{r}
# Data preparation
milk_by_region_usa <- cheese %>%
  filter(!is.na(milk) & !is.na(region) & country == "United States") %>%
  select(milk, region) %>%
  separate_rows(milk, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(milk, region) %>% 
  group_by(milk) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

milk_by_region_usa

# Plot creation
milk_by_region_usa_plot <- ggplot(
    data = milk_by_region_usa,
    aes(x = reorder(milk, -count), y = count, fill = reorder(milk, -count))
  ) + geom_col() + 
  labs(
    title = "Milk Type Usage in USA Regions",
    fill = "Milk"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
milk_by_region_usa_plot
```

## Cheese Texture Popularity in France

```{r}
# Data preparation
texture_by_region_france <- cheese %>%
  filter(!is.na(texture) & !is.na(region) & country == "France") %>%
  select(texture, region) %>%
  separate_rows(texture, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(texture, region) %>% 
  group_by(texture) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

texture_by_region_france

# Plot creation
texture_by_region_france_plot <- ggplot(
    data = texture_by_region_france,
    aes(x = reorder(texture, -count), y = count, fill = reorder(texture, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Textures Popularity in France Regions",
    fill = "Textures"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
texture_by_region_france_plot
```

## Cheese Flavor Popularity in France

```{r}
# Data preparation
flavor_by_region_france <- cheese %>%
  filter(!is.na(flavor) & !is.na(region) & country == "France") %>%
  select(flavor, region) %>%
  separate_rows(flavor, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(flavor, region) %>% 
  group_by(flavor) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

flavor_by_region_france

# Plot creation
flavor_by_region_france_plot <- ggplot(
    data = flavor_by_region_france,
    aes(x = reorder(flavor, -count), y = count, fill = reorder(flavor, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Flavor Popularity in France Regions",
    fill = "Flavors"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
flavor_by_region_france_plot
```

## Top Cheese Producers in France

```{r}
# Data preparation
producers_by_region_france <- cheese %>%
  filter(!is.na(producers) & !is.na(region) & country == "France") %>%
  select(producers, region) %>%
  separate_rows(producers, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(producers, region) %>% 
  group_by(producers) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

producers_by_region_france

# Plot creation
producers_by_region_france_plot <- ggplot(
    data = producers_by_region_france,
    aes(x = reorder(producers, -count), y = count, fill = reorder(producers, -count))
  ) + geom_col() + 
  labs(
    title = "Top Cheese Producers in France Regions",
    fill = "Producers"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
producers_by_region_france_plot
```

## Milk Type Usage in France

```{r}
# Data preparation
milk_by_region_france <- cheese %>%
  filter(!is.na(milk) & !is.na(region) & country == "France") %>%
  select(milk, region) %>%
  separate_rows(milk, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(milk, region) %>% 
  group_by(milk) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

milk_by_region_france

# Plot creation
milk_by_region_france_plot <- ggplot(
    data = milk_by_region_france,
    aes(x = reorder(milk, -count), y = count, fill = reorder(milk, -count))
  ) + geom_col() + 
  labs(
    title = "Milk Type Usage in France Regions",
    fill = "Milk"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
milk_by_region_france_plot
```

## Cheese Texture Popularity in Italy

```{r}
# Data preparation
texture_by_region_italy <- cheese %>%
  filter(!is.na(texture) & !is.na(region) & country == "Italy") %>%
  select(texture, region) %>%
  separate_rows(texture, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(texture, region) %>% 
  group_by(texture) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

texture_by_region_italy

# Plot creation
texture_by_region_italy_plot <- ggplot(
    data = texture_by_region_italy,
    aes(x = reorder(texture, -count), y = count, fill = reorder(texture, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Textures Popularity in Italy Regions",
    fill = "Textures"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
texture_by_region_italy_plot
```

## Cheese Flavor Popularity in Italy

```{r}
# Data preparation
flavor_by_region_italy <- cheese %>%
  filter(!is.na(flavor) & !is.na(region) & country == "Italy") %>%
  select(flavor, region) %>%
  separate_rows(flavor, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(flavor, region) %>% 
  group_by(flavor) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

flavor_by_region_italy

# Plot creation
flavor_by_region_italy_plot <- ggplot(
    data = flavor_by_region_italy,
    aes(x = reorder(flavor, -count), y = count, fill = reorder(flavor, -count))
  ) + geom_col() + 
  labs(
    title = "Cheese Flavor Popularity in Italy Regions",
    fill = "Flavors"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
flavor_by_region_italy_plot
```

## Top Cheese Producers in Italy

```{r}
# Data preparation
producers_by_region_italy <- cheese %>%
  filter(!is.na(producers) & !is.na(region) & country == "Italy") %>%
  select(producers, region) %>%
  separate_rows(producers, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(producers, region) %>% 
  group_by(producers) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

producers_by_region_italy

# Plot creation
producers_by_region_italy_plot <- ggplot(
    data = producers_by_region_italy,
    aes(x = reorder(producers, -count), y = count, fill = reorder(producers, -count))
  ) + geom_col() + 
  labs(
    title = "Top Cheese Producers in Italy Regions",
    fill = "Producers"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
producers_by_region_italy_plot
```

## Milk Type Usage in Italy

```{r}
# Data preparation
milk_by_region_italy <- cheese %>%
  filter(!is.na(milk) & !is.na(region) & country == "Italy") %>%
  select(milk, region) %>%
  separate_rows(milk, sep = ", ") %>%
  separate_rows(region, sep = ", ") %>%
  distinct(milk, region) %>% 
  group_by(milk) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(n = 12)

milk_by_region_italy

# Plot creation
milk_by_region_italy_plot <- ggplot(
    data = milk_by_region_italy,
    aes(x = reorder(milk, -count), y = count, fill = reorder(milk, -count))
  ) + geom_col() + 
  labs(
    title = "Milk Type Usage in Italy Regions",
    fill = "Milk"
  ) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
milk_by_region_italy_plot
```
