# Data Import and Environment Setup

```{r}
# Variable for storing the main data set
cheese <- read.csv("./dataset/cheese.csv")
# Variable for storing color scale
color_set <- scale_fill_manual(values = c(
  "#f0f", "#f08", "#f00", "#f80", "#ff0",
  "#8f0", "#0f0", "#0f8", "#0ff", "#08f",
  "#00f", "#80f"
))
theme_set <- theme(
  axis.text = element_blank(),
  axis.title = element_blank(),
  legend.background = element_rect(fill = "#444"),
  legend.title = element_text(color = "#999"),
  legend.text = element_text(color = "#999"),
  panel.background = element_rect(fill = "#444"),
  panel.grid = element_blank(),
  plot.background = element_rect(fill = "#444"),
  plot.title = element_text(color = "#999")
)
# Needed libraries
libs <- c("tidyverse", "ggplot2", "stringr")
# Libraries installation
installed_libs <- libs %in% rownames(installed.packages())
if (any(installed_libs == FALSE)) {
    install.packages(libs[!installed_libs])
}
# Libraries loading
library(tidyverse)
library(ggplot2)
library(stringr)
```

# Data Overview

## Unfiltered, as it comes within the .csv file

```{r}
cheese
```

## Cheese Distribution by Country (top 12 countries)

```{r}
# Data preparation
by_country <- cheese %>%
## Filtering out NA values and selecting only columns of interest
  filter(!is.na(cheese) & !is.na(country)) %>% 
  select(cheese, country) %>% 
## Splitting records for which country column contains multiple values
  separate_rows(country, sep = ", ") %>% 
## Selecting unique values
  distinct(cheese, country) %>% 
## Grouping and counting
  group_by(country) %>% 
  summarise(count = n()) %>%
## Sorting and trimming the data
  arrange(desc(count)) %>% 
  head(n = 12)

by_country

# Plot creation
by_country_plot <- ggplot(
    data = by_country,
    aes(x = "", y = count, fill = reorder(country, count))
  ) +
  geom_col(color = "#444") + coord_polar(theta = "y") +
  labs(
    title = "Cheese Distribution by Country",
    fill = "Countries",
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) +
  color_set + theme_set +
  theme(axis.text.x = element_text(color = "#999"))

by_country_plot
```

## Cheese Families Distribution by USA Regions (top 12 families)

```{r}
# Data preparation
families_by_region <- cheese %>%
## Filtering out NA values and selecting only columns of interest
  filter(!is.na(family) & !is.na(region) & country == "United States") %>% 
  select(family, region) %>% 
  separate_rows(region, sep = ", ") %>% 
  distinct(family, region) %>% 
  group_by(family) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(n = 12)

families_by_region

# Plot creation
families_by_region_plot <- ggplot(
  data = families_by_region,
  aes(x = reorder(family, -count), y = count, fill = reorder(family, -count))
) + geom_col() + 
labs(
  title = "Cheese Families Distribution by USA Regions",
  fill = "Families"
) + color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
families_by_region_plot
```

## Cheese Distribution by Fat Content

```{r}
# Data preparation
by_fat_content <- cheese %>%
## Filtering out NA values and selecting only columns of interest
  filter(!is.na(cheese) & !is.na(fat_content)) %>% 
  select(cheese, fat_content) %>% 
  distinct(cheese, fat_content) %>% 
  mutate(
    fat_content = ifelse(
      str_detect(fat_content, "g/100g"),
      str_replace(fat_content, " g/100g", "%"),
      fat_content
    )
  ) %>%
  filter(!str_detect(fat_content, "-")) %>% 
  mutate(
    fat_content = str_remove(fat_content, "%"),
    fat_content = as.numeric(fat_content)
  ) %>% 
  arrange(desc(fat_content))

breaks <- seq(0, ceiling(max(by_fat_content$fat_content) / 7) * 7, by = 7)

by_fat_content <- by_fat_content %>%
  mutate(fat_content_group = cut(fat_content, breaks = breaks, include.lowest = TRUE, right = FALSE)) %>% 
  group_by(fat_content_group) %>% 
  summarise(count = n())

by_fat_content

# Plot creation
by_fat_content_plot <- ggplot(
    data = by_fat_content,
    aes(x = fat_content_group, y = count, fill = fat_content_group)
  ) +
  geom_col() + 
  labs(
    title = "Cheese Distribution by Fat Content",
    fill = "Fat Content Range (%)"
  ) +
  color_set + theme_set + theme(axis.text.y = element_text(color = "#999"))
  
by_fat_content_plot
```

## Calcium Content vs. Fat Content

A scatter plot to investigate the relationship between calcium content and fat content.

## Cheese Types and Their Fat Content

A boxplot comparing fat content across different cheese types (e.g., fresh, aged).

## Vegetarian vs. Vegan Cheese Availability

A grouped bar chart comparing the number of vegetarian and vegan cheeses.

## Cheese Texture Popularity

A bar plot to visualize the frequency of different textures (e.g., soft, hard, crumbly).

## Flavor Diversity

A word cloud based on the frequency of different flavors listed in the dataset.

## Top 10 Producers by Cheese Count

A bar plot highlighting the top producers and the number of cheeses they offer.

## Regional Flavor Profiles

A heatmap showing the presence of different flavor descriptors (e.g., nutty, tangy) across regions.

## Correlation Matrix of Quantitative Variables

A correlation plot to explore relationships between variables like fat content, calcium content, and texture score.

## Cheese Families Across Countries

A treemap to visualize the distribution of cheese families (e.g., blue, brined) across different countries.

##Seasonal Color Trends If seasonality can be inferred (e.g., seasonal cheeses), use a line plot to show trends in cheese colors over time or seasons.

## Synonyms and Alternative Spellings

A network graph to display relationships between cheese synonyms and alternative spellings.

## Cheese Characteristics Radar Chart

A radar chart (or spider plot) comparing the characteristics (e.g., fat, calcium, texture) of different cheese types.

## Cheese Producers by Country

A faceted bar plot showing the number of producers in each country, with individual facets for each region.

## Milk Type Usage

A stacked bar chart or pie chart displaying the distribution of milk types (e.g., cow, goat, sheep, buffalo) used in cheeses.

## Rind Type by Cheese Family

A grouped bar chart or mosaic plot showing the relationship between rind types (e.g., natural, washed, bloomy) and cheese families.

## Cheese Color Palette

A color palette visualization (e.g., horizontal bars) to showcase the range of cheese colors, possibly sorted by type or family.

## Density of Vegan and Vegetarian Cheeses by Country

A heatmap or geographical map showing the density of vegan/vegetarian cheeses across different countries or regions.

## Flavor-Aroma Relationship

A scatterplot or bubble plot to explore the relationship between flavor descriptors and aroma descriptors.

## Top Cheese Families by Calcium Content

A lollipop chart or dot plot ranking cheese families based on their average calcium content.

## Rare Cheese Types

A Pareto chart to identify cheese types with the lowest frequency in the dataset, providing insights into unique or niche cheeses.

## Synonym Distribution

A bar chart showing the number of synonyms associated with each cheese, helping to identify cheeses with multiple aliases.

## Textural Diversity by Region

A bar chart or boxplot to compare the diversity of textures (e.g., soft, hard, crumbly) across different regions.
